---
output:
  word_document:
    toc: yes
    reference_docx: template1.docx
toc-title: 'Vocabulary paper results (v6): cumulative measures'

---

<!-- loading packages, user-defined functions and datasets -->
```{r echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE, include=FALSE}
lib <- c("tidyverse","knitr","gridExtra",
         "car","kableExtra", "magick", "grid",
         "magrittr")
lapply(lib, require, character.only = TRUE)
load(file="ws6.RData")

options(knitr.table.format = 'markdown')
```

<!-- set folder for graphs -->
```{r opts, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "images/"
)
```

<!-- additional funs -->
```{r echo = FALSE}
grid_arrange_shared_legend <- function(..., nrow = 1,y_title, x_size, y_size,widths1 = 2, widths2=0.2,hjust1=1, x_title, ncol = length(list(...)), position = c("bottom", "right")) {

  plots <- list(...)
  position <- match.arg(position)
  g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  lwidth <- sum(legend$width)
  gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
  gl <- c(gl, nrow = nrow, ncol = ncol)

  combined <- switch(position,
                     "bottom" = arrangeGrob(do.call(arrangeGrob, gl),
                                            legend,
                                            ncol = 1,
                                            heights = unit.c(unit(1, "npc") - lheight, lheight)),
                     "right" = arrangeGrob(do.call(arrangeGrob, gl),
                                           legend,
                                           ncol = 2,
                                           widths = c(widths1, widths2),
                                           left=textGrob(y_title, gp=gpar(fontsize=y_size), rot = 90),
                                           bottom=textGrob(x_title, gp=gpar(fontsize=x_size), vjust = 0, hjust = hjust1)))
  grid.newpage()
  grid.draw(combined)

}

freq_len_pp_fun <- function(df, pp_qu, le, general, freq_df, qus) {
  df_output <- df %>%
    (function(x) {
      tibble(phon = unlist(x$phon),
             ph_pr = unlist(x$ph_pr))
    })
  
  if (pp_qu == 1) {
    df_output %<>%
      filter(ph_pr < pp_qu_subtlex_us_fun26(mot_uni_on_subtlex_us$phon, chi_uni_on_subtlex_us$phon)[2])  # PP qu
  } else if (pp_qu == 2) {
    df_output %<>%
      filter(ph_pr >= pp_qu_subtlex_us_fun26(mot_uni_on_subtlex_us$phon, chi_uni_on_subtlex_us$phon)[2] & ph_pr < pp_qu_subtlex_us_fun26(mot_uni_on_subtlex_us$phon, chi_uni_on_subtlex_us$phon)[3]) # PP qu
  } else {
    df_output %<>%
      filter(ph_pr >= pp_qu_subtlex_us_fun26(mot_uni_on_subtlex_us$phon, chi_uni_on_subtlex_us$phon)[3]) # PP qu
  }
    df_output %<>%
      mutate(len = str_split(phon, "_") %>%
               sapply(length)) %>%
      filter(len == le) %>% # LEN
      mutate(UnTrn = phon)
    
    if (general == TRUE) {
      df_output %<>%
        mutate(UnTrn = UnTrn %>%
                 str_replace_all("_", ".") %>%
                 str_replace_all("UU", "AH"))
    }
    
    df_output %<>%
      left_join(freq_df, "UnTrn") %>%
      mutate(freq_qu = ifelse(SFreq < qus[2], 1,
                              ifelse(SFreq >= qus[2] & SFreq < qus[3], 2,
                                     ifelse(SFreq >= qus[3], 3, NA)))) %>%
      na.omit() %>%
      group_by(freq_qu) %>%
      summarise(n = n()) %>%
      ungroup() %>%
      mutate(perc = (n / sum(n)) * 100) %>%
      select(-n) %>%
      mutate(len = le,
             pp_t = pp_qu) 
    
    if (nrow(df_output) != 3) {
      levs <- unique(df_output$freq_qu)
      
      df_output %>%
        rbind(tibble(freq_qu = c(1:3)[!1:3 %in% levs],
                     perc = 0,
                     len = le,
                     pp_t = pp_qu))
    } else {
      df_output
    }
}

freq_len_pp_plot <- function(df, df_label, gen_par, df_freq, freq_qu_par, freq_label) {
  freq_len_pp_fun(df, pp_qu = 1, le = 2, 
                  general = gen_par, freq_df = df_freq,
                  qus = freq_qu_par) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 1, le = 3, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 1, le = 4, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 1, le = 5, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 1, le = 6, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 2, le = 2, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 2, le = 3, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 2, le = 4, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 2, le = 5, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 2, le = 6, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 3, le = 2, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 3, le = 3, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 3, le = 4, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 3, le = 5, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_pp_fun(df, pp_qu = 3, le = 6, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    mutate(len = as.factor(len),
           freq_qu = ifelse(freq_qu == 1, "T1",
                            ifelse(freq_qu == 2, "T2", "T3")) %>%
             as.factor(),
           pp_t = ifelse(pp_t == 1, "PP T1",
                         ifelse(pp_t == 2, "PP T2", "PP T3")) %>%
             as.factor()) %>%
    rename(`Phonemic length` = len,
           `Novel words (%)` = perc,
           !!freq_label := freq_qu) %>%
    (function(x) {
      if (freq_label == "Frequency") {
        ggplot(x, aes(`Phonemic length`, `Novel words (%)`)) + 
          geom_bar(aes(fill = `Frequency`), stat = "identity", position = "dodge")+
          scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 25))+
          scale_fill_grey()+
          theme(axis.text=element_text(size=20),
                axis.title=element_text(size=20),
                legend.text = element_text(size=20),
                legend.title = element_text(size = 20),
                legend.key.size = unit(1,"cm"),
                strip.text = element_text(size=20)) +
          ggtitle(df_label) +
          theme(plot.title = element_text(hjust = 0.5, size = 25)) +
          facet_grid(rows = vars(pp_t))
      } else {
        ggplot(x, aes(`Phonemic length`, `Novel words (%)`)) + 
          geom_bar(aes(fill = `Mot Frequency`), stat = "identity", position = "dodge")+
          scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 25))+
          scale_fill_grey()+
          theme(axis.text=element_text(size=20),
                axis.title=element_text(size=20),
                legend.text = element_text(size=20),
                legend.title = element_text(size = 20),
                legend.key.size = unit(1,"cm"),
                strip.text = element_text(size=20)) +
          ggtitle(df_label) +
          theme(plot.title = element_text(hjust = 0.5, size = 25)) +
          facet_grid(rows = vars(pp_t))
      }
    })
}



# frequency at each length, for each ND tertile
freq_len_nd_fun <- function(df, nd_qu, le, general, freq_df, qus) {
  df_output <- df %>%
    (function(x) {
      tibble(phon = unlist(x$phon),
             nei = unlist(x$nei))
    })
  
  if (nd_qu == 1) {
    df_output %<>%
      filter(nei < nei_qu_fun26(mot_nei_on, chi_nei_on)[2])  # ND qu
  } else if (nd_qu == 2) {
    df_output %<>%
      filter(nei >= nei_qu_fun26(mot_nei_on, chi_nei_on)[2] & nei < nei_qu_fun26(mot_nei_on, chi_nei_on)[3]) # ND qu
  } else {
    df_output %<>%
      filter(nei >= nei_qu_fun26(mot_nei_on, chi_nei_on)[3]) # ND qu
  }
  df_output %<>%
    mutate(len = str_split(phon, "_") %>%
             sapply(length)) %>%
    filter(len == le) %>% # LEN
    mutate(UnTrn = phon)
  
  if (general == TRUE) {
    df_output %<>%
      mutate(UnTrn = UnTrn %>%
               str_replace_all("_", ".") %>%
               str_replace_all("UU", "AH"))
  }
  
  df_output %<>%
    left_join(freq_df, "UnTrn") %>%
    mutate(freq_qu = ifelse(SFreq < qus[2], 1,
                            ifelse(SFreq >= qus[2] & SFreq < qus[3], 2,
                                   ifelse(SFreq >= qus[3], 3, NA)))) %>%
    na.omit() %>%
    group_by(freq_qu) %>%
    summarise(n = n()) %>%
    ungroup() %>%
    mutate(perc = (n / sum(n)) * 100) %>%
    select(-n) %>%
    mutate(len = le,
           nd_t = nd_qu) 
  
    if (nrow(df_output) != 3) {
      levs <- unique(df_output$freq_qu)
      
      df_output %>%
        rbind(tibble(freq_qu = c(1:3)[!1:3 %in% levs],
                     perc = 0,
                     len = le,
                     nd_t = nd_qu))
    } else {
      df_output
    }
}

freq_len_nd_plot <- function(df, df_label, gen_par, df_freq, freq_qu_par, freq_label) {
  freq_len_nd_fun(df, nd_qu = 1, le = 2, 
                  general = gen_par, freq_df = df_freq,
                  qus = freq_qu_par) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 1, le = 3, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 1, le = 4, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 1, le = 5, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 1, le = 6, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 2, le = 2, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 2, le = 3, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 2, le = 4, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 2, le = 5, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 2, le = 6, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 3, le = 2, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 3, le = 3, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 3, le = 4, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 3, le = 5, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    rbind(freq_len_nd_fun(df, nd_qu = 3, le = 6, 
                          general = gen_par, freq_df = df_freq,
                          qus = freq_qu_par)) %>%
    mutate(len = as.factor(len),
           freq_qu = ifelse(freq_qu == 1, "T1",
                            ifelse(freq_qu == 2, "T2", "T3")) %>%
             as.factor(),
           nd_t = ifelse(nd_t == 1, "ND T1",
                         ifelse(nd_t == 2, "ND T2", "ND T3")) %>%
             as.factor()) %>%
    rename(`Phonemic length` = len,
           `Novel words (%)` = perc,
           !!freq_label := freq_qu) %>%
    (function(x) {
      if (freq_label == "Frequency") {
        ggplot(x, aes(`Phonemic length`, `Novel words (%)`)) + 
          geom_bar(aes(fill = `Frequency`), stat = "identity", position = "dodge")+
          scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 25))+
          scale_fill_grey()+
          theme(axis.text=element_text(size=20),
                axis.title=element_text(size=20),
                legend.text = element_text(size=20),
                legend.title = element_text(size = 20),
                legend.key.size = unit(1,"cm"),
                strip.text = element_text(size=20)) +
          ggtitle(df_label) +
          theme(plot.title = element_text(hjust = 0.5, size = 25)) +
          facet_grid(rows = vars(nd_t))
      } else {
        ggplot(x, aes(`Phonemic length`, `Novel words (%)`)) + 
          geom_bar(aes(fill = `Mot Frequency`), stat = "identity", position = "dodge")+
          scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 25))+
          scale_fill_grey()+
          theme(axis.text=element_text(size=20),
                axis.title=element_text(size=20),
                legend.text = element_text(size=20),
                legend.title = element_text(size = 20),
                legend.key.size = unit(1,"cm"),
                strip.text = element_text(size=20)) +
          ggtitle(df_label) +
          theme(plot.title = element_text(hjust = 0.5, size = 25)) +
          facet_grid(rows = vars(nd_t))
      }
    })

}


# pp at each length, for each general/maternal tertile
pp_len_freq_fun <- function(df, le, df_freq, freq_qs, f_qu, general) {
  df_output <- df %>%
    (function(x) {
      tibble(phon = unlist(x$phon),
             ph_pr = unlist(x$ph_pr))
    }) %>%
    mutate(len = str_split(phon, "_") %>%
             sapply(length)) %>%
    filter(len == le) %>% # LEN
    mutate(UnTrn = phon)
  
  if (general == TRUE) {
    df_output %<>%
      mutate(UnTrn = UnTrn %>%
               str_replace_all("_", ".") %>%
               str_replace_all("UU", "AH"))
  }
  
  df_output %<>%
    left_join(df_freq, "UnTrn") %>%
    mutate(freq_qu = ifelse(SFreq < freq_qs[2], 1,
                            ifelse(SFreq >= freq_qs[2] & SFreq < freq_qs[3], 2,
                                   ifelse(SFreq >= freq_qs[3], 3, NA))))
  
  if (f_qu == 1) {
    df_output %<>%
      filter(freq_qu == 1)  # freq qu
  } else if (f_qu == 2) {
    df_output %<>%
      filter(freq_qu == 2)  # freq qu
  } else {
    df_output %<>%
      filter(freq_qu == 3)  # freq qu
  }
  
  
  df_output %<>%
    mutate(pp_qu = ifelse(ph_pr < pp_qu_subtlex_us_fun26(mot_uni_on_subtlex_us$phon, chi_uni_on_subtlex_us$phon)[2], 1,
                          ifelse(ph_pr >= pp_qu_subtlex_us_fun26(mot_uni_on_subtlex_us$phon, chi_uni_on_subtlex_us$phon)[2] & ph_pr < pp_qu_subtlex_us_fun26(mot_uni_on_subtlex_us$phon, chi_uni_on_subtlex_us$phon)[3], 2,
                                 ifelse(ph_pr >= pp_qu_subtlex_us_fun26(mot_uni_on_subtlex_us$phon, chi_uni_on_subtlex_us$phon)[3], 3, NA)))) %>%
    na.omit() %>%
    group_by(pp_qu) %>%
    summarise(n = n()) %>%
    ungroup() %>%
    mutate(len = le,
           freq_t = f_qu) 
  
  if (nrow(df_output) != 3) {
    levs <- unique(df_output$pp_qu)
    
    df_output %>%
      rbind(tibble(pp_qu = c(1:3)[!1:3 %in% levs],
                   n = 0,
                   len = le,
                   freq_t = f_qu))
  } else {
    df_output
  }
  
}

pp_len_freq_plot <- function(df_plot, freq_df, f_qs, gnrl, df_label, mot_label) {
  pp_len_freq_fun(df = df_plot, le = 2, df_freq = freq_df, 
                  freq_qs = f_qs, f_qu = 1, general = gnrl) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 3, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 1, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 4, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 1, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 5, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 1, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 6, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 1, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 2, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 2, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 3, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 2, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 4, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 2, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 5, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 2, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 6, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 2, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 2, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 3, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 3, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 3, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 4, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 3, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 5, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 3, general = gnrl)) %>%
    rbind(pp_len_freq_fun(df = df_plot, le = 6, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 3, general = gnrl)) %>%
    mutate(len = as.factor(len),
           pp_qu = ifelse(pp_qu == 1, "T1",
                          ifelse(pp_qu == 2, "T2", "T3")) %>%
             as.factor(),
           freq_t = ifelse(freq_t == 1, paste(mot_label, "Freq T1", sep = ""),
                           ifelse(freq_t == 2, paste(mot_label, "Freq T2", sep = ""), 
                                  paste(mot_label, "Freq T3", sep = ""))) %>%
             as.factor()) %>%
    rename(`Phonemic length` = len,
           `Novel words` = n,
           PP = pp_qu) %>%
    (function(x) {
      ggplot(x, aes(`Phonemic length`, `Novel words`)) + 
        geom_bar(aes(fill = `PP`), stat = "identity", position = "dodge")+
        scale_fill_grey()+
        theme(axis.text=element_text(size=20),
              axis.title=element_text(size=20),
              legend.text = element_text(size=20),
              legend.title = element_text(size = 20),
              legend.key.size = unit(1,"cm"),
              strip.text = element_text(size=15)) +
        ggtitle(df_label) +
        theme(plot.title = element_text(hjust = 0.5, size = 25)) +
        facet_grid(rows = vars(freq_t))
    })
}


# nd at each length, for each general/maternal tertile
nd_len_freq_fun <- function(df, le, df_freq, freq_qs, f_qu, general) {
  df_output <- df %>%
    (function(x) {
      tibble(phon = unlist(x$phon),
             nei = unlist(x$nei))
    }) %>%
    mutate(len = str_split(phon, "_") %>%
             sapply(length)) %>%
    filter(len == le) %>% # LEN
    mutate(UnTrn = phon)
  
  if (general == TRUE) {
    df_output %<>%
      mutate(UnTrn = UnTrn %>%
               str_replace_all("_", ".") %>%
               str_replace_all("UU", "AH"))
  }
  
  df_output %<>%
    left_join(df_freq, "UnTrn") %>%
    mutate(freq_qu = ifelse(SFreq < freq_qs[2], 1,
                            ifelse(SFreq >= freq_qs[2] & SFreq < freq_qs[3], 2,
                                   ifelse(SFreq >= freq_qs[3], 3, NA))))
  
  if (f_qu == 1) {
    df_output %<>%
      filter(freq_qu == 1)  # freq qu
  } else if (f_qu == 2) {
    df_output %<>%
      filter(freq_qu == 2)  # freq qu
  } else {
    df_output %<>%
      filter(freq_qu == 3)  # freq qu
  }
  
  
  df_output %<>%
    mutate(nd_qu = ifelse(nei < nei_qu_fun26(mot_nei_on, chi_nei_on)[2], 1,
                          ifelse(nei >= nei_qu_fun26(mot_nei_on, chi_nei_on)[2] & nei < nei_qu_fun26(mot_nei_on, chi_nei_on)[3], 2,
                                 ifelse(nei >= nei_qu_fun26(mot_nei_on, chi_nei_on)[3], 3, NA)))) %>%
    na.omit() %>%
    group_by(nd_qu) %>%
    summarise(n = n()) %>%
    ungroup() %>%
    mutate(len = le,
           freq_t = f_qu) 
  
  if (nrow(df_output) != 3) {
    levs <- unique(df_output$nd_qu)
    
    df_output %>%
      rbind(tibble(nd_qu = c(1:3)[!1:3 %in% levs],
                   n = 0,
                   len = le,
                   freq_t = f_qu))
  } else {
    df_output
  }
  
}

nd_len_freq_plot <- function(df_plot, freq_df, f_qs, gnrl, df_label, mot_label) {
  nd_len_freq_fun(df = df_plot, le = 2, df_freq = freq_df, 
                  freq_qs = f_qs, f_qu = 1, general = gnrl) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 3, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 1, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 4, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 1, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 5, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 1, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 6, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 1, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 2, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 2, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 3, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 2, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 4, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 2, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 5, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 2, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 6, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 2, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 2, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 3, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 3, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 3, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 4, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 3, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 5, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 3, general = gnrl)) %>%
    rbind(nd_len_freq_fun(df = df_plot, le = 6, df_freq = freq_df, 
                          freq_qs = f_qs, f_qu = 3, general = gnrl)) %>%
    mutate(len = as.factor(len),
           nd_qu = ifelse(nd_qu == 1, "T1",
                          ifelse(nd_qu == 2, "T2", "T3")) %>%
             as.factor(),
           freq_t = ifelse(freq_t == 1, paste(mot_label, "Freq T1", sep = ""),
                           ifelse(freq_t == 2, paste(mot_label, "Freq T2", sep = ""), 
                                  paste(mot_label, "Freq T3", sep = ""))) %>%
             as.factor()) %>%
    rename(`Phonemic length` = len,
           `Novel words` = n,
           ND = nd_qu) %>%
    (function(x) {
      ggplot(x, aes(`Phonemic length`, `Novel words`)) + 
        geom_bar(aes(fill = `ND`), stat = "identity", position = "dodge")+
        scale_fill_grey()+
        theme(axis.text=element_text(size=20),
              axis.title=element_text(size=20),
              legend.text = element_text(size=20),
              legend.title = element_text(size = 20),
              legend.key.size = unit(1,"cm"),
              strip.text = element_text(size=15)) +
        ggtitle(df_label) +
        theme(plot.title = element_text(hjust = 0.5, size = 25)) +
        facet_grid(rows = vars(freq_t))
    })
}


# frequency tertiles for lenghts 2 to 6
freq_qu_fun26 <- function(df_var1, df_var2, general) {
  tibble(phon = c(df_var1 %>% 
                    unlist(), 
                  df_var2 %>% 
                    unlist())) %>%
    mutate(len = str_split(phon, "_") %>%
             sapply(length)) %>%
    filter(len >= 2 & len <= 6) %>%
    (function(x) {
      if (general == TRUE) {
        iphod_freq %>%
          filter(UnTrn %in% (x$phon %>%
                               str_replace_all("_", ".") %>%
                               str_replace_all("UU", "AH"))) %>%
          .$SFreq %>%
          quantile(probs = c(0, 1/3, 2/3, 1), na.rm = TRUE)
      } else {
        mot_freq %>%
          filter(UnTrn %in% x$phon) %>%
          .$SFreq %>%
          quantile(probs = c(0, 1/3, 2/3, 1), na.rm = TRUE)
      }
    })
}

# ND tertiles for 2-6 lengths
nei_qu_fun26 <- function(df_var1, df_var2) {
  tibble(phon = c(df_var1 %>% 
                    unlist(), 
                  df_var2 %>% 
                    unlist())) %>%
    mutate(len = str_split(phon, "_") %>%
             sapply(length)) %>%
    filter(len >= 2 & len <= 6) %>%
    (function(x) {
        online %>%
          filter(phon %in% x$phon) %>%
          .$nei %>%
          quantile(probs = c(0, 1/3, 2/3, 1), na.rm = TRUE)

    })
}

# PP tertiles for 2-6 lengths
pp_qu_subtlex_us_fun26 <- function(df_var1, df_var2) {
  tibble(phon = c(df_var1 %>% 
                    unlist(), 
                  df_var2 %>% 
                    unlist())) %>%
    mutate(len = str_split(phon, "_") %>%
             sapply(length)) %>%
    filter(len >= 2 & len <= 6) %>%
    (function(x) {
      subtlex_us_pp %>%
        filter(Input %in% (x$phon %>%
                             str_replace_all("_", ".") %>%
                             str_replace_all("UU", "AH"))) %>%
        .$unsLBPAV %>%
        quantile(probs = c(0, 1/3, 2/3, 1), na.rm = TRUE)
  })
} 
```
<br>

# 1. Basic results

<br>

#### Table   
Unique words used by the mother and words produced by the children and model, for each stage of the input. 

```{r echo = FALSE, warning=FALSE}
summary_words <- function(df) {
  df %>%
    group_by(section) %>%
    summarise(avg_n_uni = mean(n_uni),
              sd_n_uni = sd(n_uni)) %>%
    ungroup() %>%
    round_df(0) %>%
    unite(avg_sd, c(avg_n_uni, sd_n_uni), sep = " ") %>%
    mutate(avg_sd = avg_sd %>%
             str_replace(" ", " (") %>%
             str_replace("$", ")")) %>%
    .$avg_sd
}

tibble(Stage = 1:20, 
       Child = chi_uni %>%
         summary_words(),
       Model = mod %>%
         summary_words(),
       Mother = mot_uni %>%
         summary_words()) %>%
  kable()
```


<br>

#### Table   
Words produced by each subject. Correlations for each subject considering words produced over 20 stages (N=20).

```{r table2_main, echo = FALSE, results='asis', warning=FALSE}
# different transformations were used to meet the assumption of normality (if not Spearman test was used)
table <- data.frame(Subject = unique(chi_uni$baby))
table$Chi <- chi_uni$cum_uni[which(chi_uni$section == 20)]
table$Mod <- mod$cum_uni[which(chi_uni$section == 20)]
table$Mot <- mot_uni$cum_uni[which(chi_uni$section == 20)]

for (i in unique(chi_uni$baby)[c(1, 3:6, 8:9)]) {
  test <- cor.test(log(chi_uni$n_uni[which(chi_uni$baby == i & chi_uni$section != 1)]),
                   log(mod$n_uni[which(mod$baby == i & mod$section != 1)]))
  table$r_chi.mod[table$Subject == i] <- round(test$estimate,2)
}
for (i in unique(chi_uni$baby)[c(2, 7)]) {
  test <- cor.test((chi_uni$n_uni[which(chi_uni$baby == i & chi_uni$section != 1)]),
                   (mod$n_uni[which(mod$baby == i & mod$section != 1)]), method = "spearman")
  table$r_chi.mod[table$Subject == i] <- round(test$estimate,2)
}
for (i in unique(chi_uni$baby)[c(10)]) {
  test <- cor.test(1/(chi_uni$n_uni[which(chi_uni$baby == i & chi_uni$section != 1)]),
                   1/(mod$n_uni[which(mod$baby == i & mod$section != 1)]))
  table$r_chi.mod[table$Subject == i] <- round(test$estimate,2)
}
for (i in unique(chi_uni$baby)[c(11, 12)]) {
  test <- cor.test(sqrt(chi_uni$n_uni[which(chi_uni$baby == i & chi_uni$section != 1)]),
                   sqrt(mod$n_uni[which(mod$baby == i & mod$section != 1)]))
  table$r_chi.mod[table$Subject == i] <- round(test$estimate,2)
}
for (i in unique(chi_uni$baby)) {
  table$rmse_chi.mod[table$Subject == i] <- round(rmse(chi_uni$n_uni[which(chi_uni$baby == i)] - mod$n_uni[which(mod$baby == i)]),0)
}


for (i in unique(chi_uni$baby)[c(1, 3:6, 8:9, 10, 12)]) {
  test <- cor.test(log(chi_uni$n_uni[which(chi_uni$baby == i & chi_uni$section != 1)]),
                   log(mot_uni$n_uni[which(mot_uni$baby == i & mot_uni$section != 1)]))
  table$r_chi.mot[table$Subject == i] <- round(test$estimate,2)
}
for (i in unique(chi_uni$baby)[c(11)]) {
  test <- cor.test(sqrt(chi_uni$n_uni[which(chi_uni$baby == i & chi_uni$section != 1)]),
                   sqrt(mot_uni$n_uni[which(mot_uni$baby == i & mot_uni$section != 1)]))
  table$r_chi.mot[table$Subject == i] <- round(test$estimate,2)
}
for (i in unique(chi_uni$baby)[c(2, 7)]) {
  test <- cor.test((chi_uni$n_uni[which(chi_uni$baby == i & chi_uni$section != 1)]),
                   (mot_uni$n_uni[which(mot_uni$baby == i & mot_uni$section != 1)]), method = "spearman")
  table$r_chi.mot[table$Subject == i] <- round(test$estimate,2)
}

for (i in unique(chi_uni$baby)) {
  table$rmse_chi.mot[table$Subject == i] <- round(rmse(chi_uni$n_uni[which(chi_uni$baby == i)] - mot_uni$n_uni[which(mot_uni$baby == i)]),0)
}


for (i in unique(mod$baby)[c(1, 3:6, 7, 8:9, 11, 12)]) {
  test <- cor.test(log(mod$n_uni[which(mod$baby == i & mod$section != 1)]),
                   log(mot_uni$n_uni[which(mot_uni$baby == i & mot_uni$section != 1)]))
  table$r_mod.mot[table$Subject == i] <- round(test$estimate,2)
}

for (i in unique(mod$baby)[c(2, 10)]) {
  test <- cor.test(1/(mod$n_uni[which(mod$baby == i & mod$section != 1)]),
                   1/(mot_uni$n_uni[which(mot_uni$baby == i & mot_uni$section != 1)]))
  table$r_mod.mot[table$Subject == i] <- round(test$estimate,2)
}

for (i in unique(mod$baby)) {
  table$rmse_mod.mot[table$Subject == i] <- round(rmse(mod$n_uni[which(mod$baby == i)] - mot_uni$n_uni[which(mot_uni$baby == i)]),0)
}

means_table <- data.frame(Subject = "MEAN", Chi = mean(table$Chi), Mod = mean(table$Mod), 
                          Mot = mean(table$Mot), r_chi.mod = "-", rmse_chi.mod = round(mean(table$rmse_chi.mod),0),
                          r_chi.mot = "-", rmse_chi.mot = round(mean(table$rmse_chi.mot),0), r_mod.mot = "-", rmse_mod.mot = round(mean(table$rmse_mod.mot),0) )
table <- rbind(table, means_table)
table$Chi <- round(table$Chi,0); table$Mod <- round(table$Mod,0);table$Mot <- round(table$Mot,0)
kable(table)
```

<br>

Words that children have produced differently from model and mothers (percentages) and vice versa. Words that mothers have produced differently from model.

```{r diff_words_main, echo=FALSE}
table <- data.frame(id = c(unique(chi_uni$baby), "MEAN"),
                    chi_not_mod = c(rep(NA, length(unique(chi_uni$baby))),NA),
                    mod_not_chi = c(rep(NA, length(unique(chi_uni$baby))),NA),
                    chi_not_mot = c(rep(NA, length(unique(chi_uni$baby))),NA),
                    mot_not_chi = c(rep(NA, length(unique(chi_uni$baby))),NA),
                    mot_not_mod = c(rep(NA, length(unique(chi_uni$baby))),NA),
                    stringsAsFactors = F)

for (i in table$id[-nrow(table)]) {
  chi_uni_sub <- chi_uni %>% filter(baby  == i)
  mod_sub <- mod %>% filter(baby  == i)
  mot_uni_sub <- mot_uni %>% filter(baby  == i)
  
  table$chi_not_mod[which(table$id == i)] <- (sum(!unique(unlist(chi_uni_sub$phon)) %in% unique(unlist(mod_sub$phon))) / 
  length(unique(unlist(chi_uni_sub$phon))))*100
  
  table$mod_not_chi[which(table$id == i)] <- (sum(!unique(unlist(mod_sub$phon)) %in% unique(unlist(chi_uni_sub$phon))) / 
  length(unique(unlist(mod_sub$phon))))*100
  
    table$chi_not_mot[which(table$id == i)] <- (sum(!unique(unlist(chi_uni_sub$phon)) %in% unique(unlist(mot_uni_sub$phon))) / 
  length(unique(unlist(chi_uni_sub$phon))))*100
  
  table$mot_not_chi[which(table$id == i)] <- (sum(!unique(unlist(mot_uni_sub$phon)) %in% unique(unlist(chi_uni_sub$phon))) / 
  length(unique(unlist(mot_uni_sub$phon))))*100
  
  table$mot_not_mod[which(table$id == i)] <- (sum(!unique(unlist(mot_uni_sub$phon)) %in% unique(unlist(mod_sub$phon))) / 
  length(unique(unlist(mot_uni_sub$phon))))*100
  
}

table$chi_not_mod[which(table$id == "MEAN")] <- mean(table$chi_not_mod[-nrow(table)])
table$mod_not_chi[which(table$id == "MEAN")] <- mean(table$mod_not_chi[-nrow(table)])
table$chi_not_mot[which(table$id == "MEAN")] <- mean(table$chi_not_mot[-nrow(table)])
table$mot_not_chi[which(table$id == "MEAN")] <- mean(table$mot_not_chi[-nrow(table)])
table$mot_not_mod[which(table$id == "MEAN")] <- mean(table$mot_not_mod[-nrow(table)])

round_df <- function(df, digits) {
  nums <- vapply(df, is.numeric, FUN.VALUE = logical(1))

  df[,nums] <- round(df[,nums], digits = digits)

  (df)
}

table <- round_df(table, 2)

kable(table)
```


<br>


# 2. Child data

## 2.1 Simple effects

Cumulative number of words learned considered

<br>

### 2.1.1 Syllabic Length

```{r child_length, echo = FALSE, results='asis', fig.width=15, fig.height=8}
plot_syll_length <- function(df, df_label) {
  ggplot(df, aes(x=section, y=len_1_cum, fill=baby, shape="1 syll")) + 
  geom_point(size=4, alpha=0.4) +
  scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
  labs(x = "Stage", y = "Cumulative novel words") +
  ggtitle(df_label) +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) +
  geom_point(aes(x=section, y=len_2_cum, fill=baby, shape="2 syll"),size=4,alpha=0.4) + 
  geom_point(aes(x=section, y=len_3_cum, fill=baby, shape="3 syll"),size=4,alpha=0.4) + 
  scale_shape_manual("", values=c(`1 syll`= 0, `2 syll`= 3, `3 syll` = 2))+
  guides(fill=FALSE, alpha=F)+
  geom_smooth(aes(x=section, y=len_1_cum), fill=NA, colour="black", method="lm",linetype="dotted")+
  geom_smooth(aes(x=section, y=len_2_cum), fill=NA, colour="black", method="lm",linetype="dotted")+
  geom_smooth(aes(x=section, y=len_3_cum), fill=NA, colour="black", method="lm",linetype="dotted")+
  theme(axis.text=element_text(size=18),
        axis.title = element_text(size=20),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 20),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)))+  
  scale_colour_grey(start = 0, end = .9)
}

plot1 <- plot_syll_length(chi_uni, "") 
#plot2 <- plot_syll_length(mod, "Model") 
#plot3 <- plot_syll_length(mot_uni, "Mothers") 

#grid_arrange_shared_legend(plot3, plot1, plot2, position = "right", 
#                           x_title = "Stage", y_title = "Novel words (%)",
#                           x_size = 25, y_size = 25)

plot1
```

**Figure .** Cumulative unique words (e.g., those words produced at stage 3 that were not present in any previous stage) that are one-syllable, two-syllable, and three-syllable at each stage of the mother and child transcriptions and model’s learning.

<br>

### 2.1.2 PP

IPhOD Weighted phonotactic probability measure based on written log (base 10) word frequencies from the [SUBTLEXus database](https://www.ugent.be/pp/experimentele-psychologie/en/research/documents/subtlexus) (Brysbaert & New, 2009). 

<br>

#### Quantiles table

```{r echo = FALSE, message=FALSE, warning=FALSE}
pp_qu_subtlex_us %>%
  as.matrix() %>%
  t() %>%
  kable()
```

<br>

```{r child_pp, echo = FALSE, results='asis', fig.width=15, fig.height=8}
plot_pp <- function(df, main_title) {
  ggplot(df, aes(x=section, y=ph_pr_qu1_cum, fill=baby, shape="T1")) + 
  geom_point(size=4, alpha=0.4) +
  scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
  labs(x = "Stage", y = "Cumulative novel words") +
  ggtitle(main_title) +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) +
  geom_point(aes(x=section, y=ph_pr_qu2_cum, fill=baby, shape="T2"),size=4, alpha=0.4) + 
  geom_point(aes(x=section, y=ph_pr_qu3_cum, fill=baby, shape="T3"), size=4,alpha=0.4) + 
  scale_shape_manual("PP tertile", values=c(`T1`= 0, `T2`= 3, `T3` = 2),
                     breaks=c("T1","T2", "T3"))+
  guides(fill=FALSE)+
  geom_smooth(aes(x=section, y=ph_pr_qu1_cum,linetype="T1"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=ph_pr_qu2_cum,linetype="T2"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=ph_pr_qu3_cum,linetype="T3"), fill=NA, colour="black", method="lm", size=0.8)+
  theme(axis.text=element_text(size=18),  
        axis.title = element_text(size=20),
        legend.text = element_text(size = 20),         
        legend.title = element_text(size = 20),         
        legend.key.size = unit(1, "cm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)))+     
    scale_colour_grey(start = 0, end = .9)+
  scale_linetype_manual("PP tertile", 
                        values=c(`T1` = "longdash",`T2` = "solid", `T3`= "dotted"),
                        breaks=c("T1","T2", "T3"))
}

plot1 <- plot_pp(chi_uni_on_subtlex_us, "") 
#plot2 <- plot_pp(mod_on_subtlex_us, "Model") 
#plot3 <- plot_pp(mot_uni_on_subtlex_us, "Mothers") 

#grid_arrange_shared_legend(plot3, plot1, plot2, position = "right", 
#                           x_title = "Stage", y_title = "Novel words (%)",
#                           x_size = 25, y_size = 25,
#                           widths1 = 2, widths2 = 0.5, hjust1 = 1)
plot1
```

**Figure .** Breakdown of PP by tertile

<br>

### 2.1.3 ND

#### Quantiles table

```{r echo = FALSE, message=FALSE, warning=FALSE}
nei_qu %>%
  as.matrix() %>%
  t() %>%
  kable()
```

<br>

```{r child_nei, echo = FALSE, results='asis', fig.width=16, fig.height=9}
plot_nei <- function(df, main_title) {
  ggplot(df, aes(x=section, y=nei_qu1_cum, fill=baby, shape="T1")) + 
  geom_point(size=4, alpha=0.2) +
  scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
  labs(x = "Stage", y = "Cumulative novel words") +
  ggtitle(main_title) +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) +
  geom_point(aes(x=section, y=nei_qu2_cum, fill=baby, shape="T2"), size=4,alpha=0.2) + 
  geom_point(aes(x=section, y=nei_qu3_cum, fill=baby, shape="T3"), size=4,alpha=0.2) + 
  scale_shape_manual("ND Tertile", values=c(`T1`= 0, `T2`= 3, `T3` = 2),
                     breaks=c("T3","T2","T1"))+
  guides(fill=FALSE)+
  geom_smooth(aes(x=section, y=nei_qu1_cum,linetype="T1"), 
              fill=NA, colour="black", method="lm", size=0.8) +
  geom_smooth(aes(x=section, y=nei_qu2_cum,linetype="T2"), 
              fill=NA, colour="black", method="lm", size=0.8) +
  geom_smooth(aes(x=section, y=nei_qu3_cum,linetype="T3"), 
              fill=NA, colour="black", method="lm", size=0.8) +
  theme(axis.text=element_text(size=18),  
        axis.title = element_text(size=20),
        legend.text = element_text(size = 20),         
        legend.title = element_text(size = 20),         
        legend.key.size = unit(1, "cm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0)))+      
    scale_colour_grey(start = 0, end = .9) +
  scale_linetype_manual("ND Tertile", 
                        values=c(`T1` = "longdash",
                                 `T2` = "solid", `T3`= "dotted"), 
                        breaks=c("T3","T2","T1"))
}

plot1 <- plot_nei(chi_nei_on, "") 
#plot2 <- plot_nei(mod_nei_on, "Model") 
#plot3 <- plot_nei(mot_nei_on, "Mothers") 

#grid_arrange_shared_legend(plot3, plot1, plot2, position = "right", 
#                           x_title = "Stage", y_title = "Novel words (%)",
#                           x_size = 25, y_size = 25,
#                           widths1 = 2, widths2 = 0.5, hjust1 = 1)
plot1
```

**Figure .** Breakdown of ND by tertile

<br>

### 2.1.4 Frequency

IPhOD General Frequency measure based on [SUBTLEXus](https://www.ugent.be/pp/experimentele-psychologie/en/research/documents/subtlexus) (Brysbaert & New, 2009). 
Words that are not present in IPhOD have no frequency value and were therefore excluded.

<br>

#### Quantiles table

```{r echo = FALSE, message=FALSE, warning=FALSE}
freq_qus %>%
  as.matrix() %>%
  t() %>%
  kable()
```

<br>

```{r child_freq, echo = FALSE, results='asis', fig.width=16, fig.height=9}
plot_freq <- function(df, main_title, tertile = "IPhOD Tertile") {
  ggplot(df, aes(x=section, y=freq_qu1_cum, fill=baby, shape="T1")) + 
  geom_point(size=4, alpha=0.2) +
  scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
  labs(x = "Stage", y = "Cumulative novel words") +
  ggtitle(main_title) +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) +
  geom_point(aes(x=section, y=freq_qu2_cum, fill=baby, shape="T2"),size=4, alpha=0.2) + 
  geom_point(aes(x=section, y=freq_qu3_cum, fill=baby, shape="T3"), size=4,alpha=0.2) + 
  scale_shape_manual(tertile, values=c(`T1`= 0, `T2`= 3, `T3` = 2),
                     breaks=c("T3", "T2","T1")) +
  guides(fill=FALSE)+
  geom_smooth(aes(x=section, y=freq_qu1_cum,linetype="T1"), 
              fill=NA, colour="black", method="lm", size=0.8) +
  geom_smooth(aes(x=section, y=freq_qu2_cum,linetype="T2"), 
              fill=NA, colour="black", method="lm", size=0.8) +
  geom_smooth(aes(x=section, y=freq_qu3_cum,linetype="T3"), 
              fill=NA, colour="black", method="lm", size=0.8) +
  theme(axis.text=element_text(size=18),  
        axis.title = element_text(size=20),
        legend.text = element_text(size = 20),         
        legend.title = element_text(size = 20),         
        legend.key.size = unit(1, "cm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0))) +    
  scale_colour_grey(start = 0, end = .9) +
  scale_linetype_manual(tertile, 
                        values=c(`T1` = "longdash",
                                 `T2` = "solid", `T3`= "dotted"),
                        breaks=c("T3", "T2","T1"))
}

plot1 <- plot_freq(chi_uni_on_freq, "") 
#plot2 <- plot_freq(mod_on_freq, "Model") 
#plot3 <- plot_freq(mot_uni_on_freq, "Mothers") 

#grid_arrange_shared_legend(plot3, plot1, plot2, position = "right", 
#                           x_title = "Stage", y_title = "Novel words (%)",
#                           x_size = 25, y_size = 25,
#                           widths1 = 2, widths2 = 0.5, hjust1 = 1)
plot1
```

**Figure.** Breakdown of General frequency by tertile

<br>

## 2.2 Controlling for length

### 2.2.1 PP at each phonemic word length (raw counts)

<br>

```{r child_pp_length, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_prop <- function(list_dfs, df_label) {
  list_dfs[[df_label]] %>%     
    summarise(sum(ph_pr_qu1), sum(ph_pr_qu2), sum(ph_pr_qu3)) %>%
    {.} %>%
    unlist()
}

table <- tibble(`Phonemic length` = c(rep(2,3), rep(3,3), 
                                      rep(4,3), rep(5,3), 
                                      rep(6,3)) %>%
                  as.factor(),
                `PP tertile` = rep(c("T1","T2","T3"),5) %>%
                  as.factor(),
                `Novel words`= c(table_prop(log_pp_lengths, "chi_uni_len2"),
                                     table_prop(log_pp_lengths, "chi_uni_len3"), 
                                     table_prop(log_pp_lengths, "chi_uni_len4"),
                                     table_prop(log_pp_lengths, "chi_uni_len5"), 
                                     table_prop(log_pp_lengths, "chi_uni_len6")))

pp_at_length_plot <- function(df, df_label) {
  ggplot(df, aes(`Phonemic length`, `Novel words`)) + 
  geom_bar(aes(fill = `PP tertile`), stat = "identity", position = "dodge")+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0))) +    
  ggtitle(df_label) +
  theme(plot.title = element_text(hjust = 0.5, size = 25))
}

pp_at_length_plot(table, "")
```

**Figure .** CHILD breakdown with tertiles computed for 2-6 phonemes across all mother and child words, using the same tertiles to breakdown each length

<br>

### 2.2.2 ND at each phonemic length (raw counts)

<br>

```{r child_nd_length, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_prop <- function(list_dfs, df_label) {
  list_dfs[[df_label]] %>%     
    summarise(sum(nei_qu1), sum(nei_qu2), sum(nei_qu3)) %>%
    {.} %>%
    unlist()
}

table <- tibble(`Phonemic length` = c(rep(2,3), rep(3,3), 
                                      rep(4,3), rep(5,3), 
                                      rep(6,3)) %>%
                  as.factor(),
                `ND tertile` = rep(c("T1","T2","T3"),5) %>%
                  as.factor(),
                `Novel words`= c(table_prop(nd_lengths, "chi_uni_len2"),
                                     table_prop(nd_lengths, "chi_uni_len3"), 
                                     table_prop(nd_lengths, "chi_uni_len4"),
                                     table_prop(nd_lengths, "chi_uni_len5"), 
                                     table_prop(nd_lengths, "chi_uni_len6")))

nd_at_length_plot <- function(df, df_label) {
  ggplot(df, aes(`Phonemic length`, `Novel words`)) + 
  geom_bar(aes(fill = `ND tertile`), stat = "identity", position = "dodge")+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0))) +   
  ggtitle(df_label) +
  theme(plot.title = element_text(hjust = 0.5, size = 25))
}

nd_at_length_plot(table, "")
```
**Figure.** Novel words learned in each neighbourhood density tertile by phonemic length. Tertiles are based on the whole dataset of two to six phoneme words. 

<br>

## 2.3 Controlling for frequency

### 2.3.1 PP at each frequency tertile (raw counts)

<br>

```{r pp_freq_1, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_prop <- function(list_dfs, df_label) {
  list_dfs[[df_label]] %>%     
    summarise(sum(ph_pr_qu1), sum(ph_pr_qu2), sum(ph_pr_qu3)) %>%
    {.} %>%
    unlist()
}

table <- tibble(`General Frequency` = c(rep(1,3),rep(2,3),rep(3,3)) %>%
                  as.factor(),
                `PP tertile` = rep(c("T1","T2","T3"),3) %>%
                  as.factor(),
                `Novel words`= c(table_prop(pp_freqs, "chi_pp_freq1"),
                                     table_prop(pp_freqs, "chi_pp_freq2"), 
                                     table_prop(pp_freqs, "chi_pp_freq3")))

pp_at_freq_plot <- function(df, df_label) {
  ggplot(df, aes(`General Frequency`, `Novel words`)) + 
  geom_bar(aes(fill = `PP tertile`), stat = "identity", position = "dodge")+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0))) +   
  ggtitle(df_label) +
  theme(plot.title = element_text(hjust = 0.5, size = 25))
}

pp_at_freq_plot(table, "")
```

**Figure .** Child novel words in each LOG PP tertile across general frequency tertiles

### 2.3.2 ND at each frequency tertile (raw counts)

<br>

```{r nei_freq_1, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_prop <- function(list_dfs, df_label) {
  list_dfs[[df_label]] %>%     
    summarise(sum(nei_qu1), sum(nei_qu2), sum(nei_qu3)) %>%
    {.} %>%
    unlist()
}

table <- tibble(`General Frequency` = c(rep(1,3),rep(2,3),rep(3,3)) %>%
                  as.factor(),
                `ND tertile` = rep(c("T1","T2","T3"),3) %>%
                  as.factor(),
                `Novel words`= c(table_prop(nei_freqs, "chi_nei_freq1"),
                                     table_prop(nei_freqs, "chi_nei_freq2"), 
                                     table_prop(nei_freqs, "chi_nei_freq3")))

nd_at_freq_plot <- function(df, df_label) {
  ggplot(df, aes(`General Frequency`, `Novel words`)) + 
  geom_bar(aes(fill = `ND tertile`), stat = "identity", position = "dodge")+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"),
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 15, r = 0, b = 0, l = 0))) +   
  ggtitle(df_label) +
  theme(plot.title = element_text(hjust = 0.5, size = 25))
}

nd_at_freq_plot(table, "")
```

**Figure .** Child novel words in each ND tertile across general frequency tertiles